Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-04-03 doc/supplementary_information.Rmd
updated SI plots
updated SI with some fig titles

## Species traits and correlations

![](display/Fig_SI_species_sensitivities.png)

![](display/Fig_SI_sensitivity_cor_dec.png)

![](display/Fig_trait_intercept_plot.png)

## Individual growth and correlations

- Negative growth proportions across the years

![](display/sens_corr.png)

@@

>>>>

## Growth timeseries and anomalies

![Fig S3: Growth anomalies across the timeseries](display/growth_anom_fullseries.png)

![Fig S4: Proportion of negative growth increments](display/neg_incs.png)

## Drought year growth of species and individuals

![Fig S4: Species sensitivities in drought years](display/Fig_SI_species_sensitivities.png)

![Fig S5: Correlations of species sensitivities across the two years](display/Fig_SI_sensitivity_cor_dec.png)

<!-- ![](display/Fig_trait_intercept_plot.png) -->

![Fig S6: Correlation of individual sensitivities across the two years](display/sens_corr.png)

@@

- Conditional dependence of variables
